### 2024-06-11 manuscript.Rmd
some json formatting

```{r echo=FALSE, eval=TRUE, results="asis"}
jsonlite::serializeJSON(numbers_ex, pretty=TRUE)
```

@@

```{r echo=FALSE, eval=TRUE, results="asis"}
jsonlite::serializeJSON(digest::digest(numbers_ex,algo = "sha256"),pretty=TRUE)
```

In addition to the contents of all newly declared variables in a `reproducibleR`-chunk, the package also stores fingerprints of the code syntax.
This is shown in the schematic in Figure \@ref(ref:jsonschema).
```{r jsonschema, fig.cap="(ref:jsonschema)A JSON file stores fingerprints of all newly declared variables in a reproducibleR-chunk as well as fingerprints of the code chunk syntax."}
knitr::include_graphics("img/schema-json-fingerprints.png")

@@

>>>>

```{r echo=FALSE, eval=TRUE, results="asis"}
content <- jsonlite::serializeJSON(numbers_ex, pretty=TRUE)
content <- gsub(pattern="\\n",replacement="  \n", x=content)
cat(content)
```

@@

```{r echo=FALSE, eval=TRUE, results="asis"}
content <- jsonlite::serializeJSON(digest::digest(numbers_ex,algo = "sha256"),pretty=TRUE)
content <- gsub(pattern="\\n",replacement="  \n", x=content)
cat(content)
```

```{r jsonschema, fig.cap="(ref:jsonschema) A JSON file stores fingerprints of all newly declared variables in a reproducibleR-chunk as well as fingerprints of the code chunk syntax."}
knitr::include_graphics("img/schema-json-fingerprints.png")

@@

In addition to the contents of all newly declared variables in a `reproducibleR`-chunk, the package also stores fingerprints of the code syntax.
This is shown in the schematic in Figure \@ref(jsonschema).
